### 2020-10-14 Thesis-Chapter3-Arguments.tex
Reoutline Chapter 3

\chapter{Arguments}
\label{chap-arguments}

@@

Wicked problems. \ac{OODAloop}.

@@

\subsection{Encryption and Exceptional Access as a Wicked Problem}

\subsection{Approaches to Solving Wicked Problems}

\subsubsection{Failure of the Classical Analytic Method}

\subsubsection{Muddling Through}

\subsubsection{Pitfalls to Avoid}

- Easy answers
  - EA mandates, complexity denial
- Fallacies!
- Bad results with long technical tails

\subsection{Plan for this Chapter}

% - But we're _exactly_ following the classical analytic method! Well, yes, but in a cooperative manner, knowing it will
%     require iteration, and being careful about side effects. It's an agile approach to policy making, but it's still
%     policy making.
% Already covered defining the problem. Next will discuss goals and list alternatives. That will feed into threat
% modeling.

\section{Desireable Outcomes}

@@

\section{Proposed Alternatives}

>>>>

\chapter{Wicked Problems and the EA Debate}
\label{chap-arguments}

Before going into detail about the arguments used in the \ac{EA} debate, it is worth studying \acp{wicked-prob} in
greater detail. What are they, and why is the case of encryption, privacy, and \ac{EA} in this category? What approaches
to tackling \acp{wicked-prob} succeed and fail? How can we collectively situation ourselves to make real progress? This
chapter seeks to answer these questions.

@@

\subsection{Characteristics}

\subsection{Encryption and EA as a Wicked Problem}

\section{Failure of Current Policymaking Approaches}

\subsection{The Classical Analytical Method}

\subsection{Muddling Through}

\subsection{Lessons}

- Avoid pitfalls of
  - Easy answers
    - EA mandates, complexity denial
  - Fallacies!
  - Bad results with long technical tails

\section{Proposal: The OODA Loop for Policymaking}

\ac{OODAloop}.

@@

% Already covered defining the problem. Next will discuss goals and list alternatives. That will feed into threat
% modeling

\section{Mapping the EA Debate}

\subsection{Desireable Outcomes}

@@

\subsection{Proposed Alternatives}
